HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ondrej's comments and fixes

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
%\usepackage{subfigure}
\usepackage{pgfplotstable}
\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}

@@

@@

\paragraph{UCCA Annotation.}
We begin by creating UCCA annotations for the source sentence, following the
UCCA guidelines\footnote{All UCCA-related resources can be found
  here: \url{http://www.cs.huji.ac.il/~oabend/ucca.html}}.
Let $L$ be the set of possible UCCA labels.
Given a sentence $s = (w_1, \ldots,w_n)$, the UCCA annotation is a DAG $G=(V,E,\ell)$,
where $\ell: V \rightarrow L$, and where $W = \{w_1,\ldots,w_n\}$ correspond to the leaves of $G$.
For every node $v \in V$, we define its {\it yield} $yld(v)$ as $v$'s descendants in $W$.
The semantic units for a sentence $s$, induced by the annotation $G$
is the set of yields of nodes in $V$. We denote it with $Units(s)$ for brevity.
We note that the translation need not be annotated.

@@

We proceed to detailing how judgements on the semantic units
of the source are aggregated into a composite score.
While future extensive empirical evaluation with HUME, and using it to
tune MT systems may suggest more complex measure,
as a starting point we take a parsimonious approach
and define aggregation of the judgements.

Let $Correct(s,t)$ be the number of atomic units in $s$ marked as Green relative to $t$ plus
the number of structural units in $s$ marked as Adequate relative to $t$.
Let $Partial(s,t)$ be the number of atomic units in $s$ marked as Orange relative
to $t$. Then HUME's composite score is:

\vspace{-.5cm}
\begin{equation}
  \small
  HUME(s,t) = \frac{Correct(s,t) + 0.5\cdot Partial(s,t)}{|Units(s)|}
\end{equation}

>>>>

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
%\usepackage{subfigure}
\usepackage{pgfplotstable}
\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}

@@

% better maths typography
\def\setsize#1{\lvert #1 \rvert}
\def\func#1{\text{\it #1}}  % much better kerning within function names
\def\HUME{\func{HUME}}
\def\Correct{\func{Correct}}
\def\Partial{\func{Partial}}
\def\Units{\func{Units}}

@@

\paragraph{UCCA Annotation.}
We begin by creating UCCA annotations for the source sentence, following the
UCCA guidelines\footnote{All UCCA-related resources can be found
  here: \url{http://www.cs.huji.ac.il/~oabend/ucca.html}}.
Let $L$ be the set of possible UCCA labels.
Given a sentence $s = (w_1, \ldots,w_n)$, the UCCA annotation is a DAG $G=(V,E,\ell)$,
where $\ell: V \rightarrow L$, and where $W = \{w_1,\ldots,w_n\}$ correspond to the leaves of $G$.
For every node $v \in V$, we define its {\it yield} $yld(v)$ as $v$'s descendants in $W$.
The semantic units for a sentence $s$, induced by the annotation $G$
is the set of yields of nodes in $V$. We denote it with $\Units(s)$ for brevity.
We note that the translation need not be annotated.

@@

We proceed to detailing how judgements on the semantic units
of the source are aggregated into a composite score.
While future extensive empirical evaluation with HUME and its application to MT
system tuning may suggest more complex definition,
as a starting point we take a parsimonious approach
and simply aggregate the judgements.

Let $\Correct(s,t)$ be the number of atomic units in $s$ marked as Green relative to $t$ plus
the number of structural units in $s$ marked as Adequate relative to $t$.
Let $\Partial(s,t)$ be the number of atomic units in $s$ marked as Orange relative
to $t$. Then HUME's composite score is:

\vspace{-.5cm}
\begin{equation}
  \small
  \HUME(s,t) = \frac{\Correct(s,t) + 0.5\cdot \Partial(s,t)}{\setsize{\Units(s)}}
\end{equation}
